DOpElib:\\ Differential Equations and Optimization Environment

### 2018-08-06 Examples/Documentation/introduction.tex
Some modifications in the documention: institute TW, more remarks about draps when installing dope, etc.

\newpage
\section{References}
If you like the library and use it for your own projects, please give credits by 
referencing the project \dope{}~\cite{dope} using the following bibtex entries:

@@

\section{Contributors \& Developers}
\label{sec:contrib}
The library is currently maintained by 
\begin{itemize}
  \item Thomas Wick (Centre de Mathématiques Appliquées (CMAP) École Polytechnique)
  \item Winnifried Wollner (Technische Universität Darmstadt)
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Installation}\label{sec_installation}
To work with DOpElib, your need necessarily deal.II, which installation 
we describe first. Afterwards, the DOpElib installation is described and finally
other optional packages might be installed.
\begin{itemize}
\item We automatically search for \texttt{deal.II} to your home
  directory, i.e., if \texttt{deal.II} is located in \\
\texttt{\textasciitilde/deal.II} you don't have to do anything. 
\item Alternatively, if you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
\begin{remark}
\textbf{Be careful} if you work in several terminal windows and have several deal.II versions. In this case, the
export-command might have to be done again in that new window. Otherwise
another deal.II version might be linked resulting in linker errors or
segmentation faults without useful error message. In order to check to which
deal.II version DOpE is linked, type 
\begin{lstlisting}
echo ${DEAL_II_DIR}
\end{lstlisting}
in the current terminal window.
\end{remark}
Detailed installing instructions for deal.II (here the last version
8.4.0) can be found on 
\texttt{http://www.dealii.org/8.4.0/readme.html}. The deal.II 
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item If you obtained a tar-ball, unpack in your preferred directory:
\begin{lstlisting}
 tar -xzf dopelib-4.0.tar.gz
\end{lstlisting}
to get a directory 
\begin{lstlisting}
dopelib-4.0/
\end{lstlisting}
containing the source files. If you cloned the git repository you
already have a directory; \texttt{dopelib} by default, containing the sources.
\item Change to the directory with the sources, and then to the
  subdirectory \texttt{DOpEsrc}.
Once there, to build \texttt{DOpElib} you can call 
\begin{lstlisting}
 make c-all
\end{lstlisting}
to build and configure the library using cmake. 
You also get various alternatives by just typing 
\texttt{make}, including the generation of the documentation.
Building the documentation will require  
latex or doxygen to be installed on your computer.
\item If your would like to check the examples, change to the
  subfolder \texttt{Examples} from the main source directory.
Typing 
\begin{lstlisting}
make
\end{lstlisting}
will again provide you with the available options:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    c-all     :  Make all examples using cmake                           =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    c-cat     :  Run clean, run c-all, run tests (combine these commands)=
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
The options are $c-all$ and $c-cat$ utilizing the cmake build system
to create the executables (and optionally run the tests if all went well).

@@

\end{itemize}
\section{FAQs}
\paragraph{1.) When building the library I get an error message:}
\begin{itemize}
\item \textbf{unrecognized command line option "-std=c++11"}\\
  This means that your compiler is too old. You can check the 
  version of your compiler using \texttt{g++ -v}. If the version is lower than
  \texttt{4.8} you need to get a newer compiler version.
\end{itemize}

>>>>

\newpage
\section{References}
If you like the library and use it for your own projects, please give credits by 
referencing the project \dope{} using the following bibtex entries \cite{dope,dopelib}

@@

\section{Contributors \& Developers}
\label{sec:contrib}
The library is currently maintained by 
\begin{itemize}
  \item Thomas Wick (Leibniz Universit\"at Hannover)
  \item Winnifried Wollner (Technische Universität Darmstadt)
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Installation}\label{sec_installation}
To work with DOpElib, your need necessarily deal.II, which installation 
we describe first. Afterwards, the DOpElib installation is described and finally
other optional packages might be installed.
\begin{itemize}
\item We automatically search for \texttt{deal.II} to your home
  directory, i.e., if \texttt{deal.II} is located in \\
\texttt{\textasciitilde/deal.II} you don't have to do anything. 
\item Alternatively, if you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
\begin{remark}
\textbf{Be careful} if you work in several terminal windows and have several deal.II versions. In this case, the
export-command might have to be done again in that new window. Otherwise
another deal.II version might be linked resulting in linker errors or
segmentation faults without useful error message. In order to check to which
deal.II version DOpE is linked, type 
\begin{lstlisting}
echo ${DEAL_II_DIR}
\end{lstlisting}
in the current terminal window.
\end{remark}
\begin{remark}
\textbf{Furthermore:} please make sure that you point in the above path 
to the deal.II \texttt{install} folder and NOT in the main directory of your deal.II 
installation.
\end{remark}

Detailed installing instructions for deal.II (here the last version
8.4.0) can be found on 
\texttt{http://www.dealii.org/8.4.0/readme.html}. The deal.II 
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%

%
\item Get a copy of \texttt{DOpElib}, see Section~\ref{sec:obtain} for details.
%
\item If you obtained a tar-ball, unpack in your preferred directory:
\begin{lstlisting}
 tar -xzf dopelib-4.0.tar.gz
\end{lstlisting}
to get a directory 
\begin{lstlisting}
dopelib-4.0/
\end{lstlisting}
containing the source files. If you cloned the git repository you
already have a directory; \texttt{dopelib} by default, containing the sources.
\item Change to the directory with the sources, and then to the
  subdirectory \texttt{DOpEsrc}.
Once there, to build \texttt{DOpElib} you can call 
\begin{lstlisting}
 make c-all
\end{lstlisting}
to build and configure the library using cmake. 
\begin{remark}
Due to very frequent problems at this stage, we strongly recommend 
to read first now Section \ref{sec_FAQ} before yielding to despair.
\end{remark}

You also get various alternatives by just typing 
\texttt{make}, including the generation of the documentation.
Building the documentation will require  
latex or doxygen to be installed on your computer.
\item If your would like to check the examples, change to the
  subfolder \texttt{Examples} from the main source directory.
Typing 
\begin{lstlisting}
make
\end{lstlisting}
will again provide you with the available options:
{\footnotesize
\begin{lstlisting}
===========================================================================
=              Makefile for the DOpE documentation                        =
===========================================================================
=                                                                         =
= The following targets exist:                                            =
=    c-all     :  Make all examples using cmake                           =
=    clean     :  Cleaning up all examples                                =
=    tests     :  Run all test param data.                                =
=    c-cat     :  Run clean, run c-all, run tests (combine these commands)=
=    doc       :  Create documentation in pdf file format via latexmk     =
=    distclean :  Cleaning up, including documentation                    =
=    warncheck :  Checks whether all Examples compile without warnings    =
===========================================================================
\end{lstlisting}
}
The options are $c-all$ and $c-cat$ utilizing the cmake build system
to create the executables (and optionally run the tests if all went well).

@@

\end{itemize}
\section{FAQs}
\label{sec_FAQ}
\paragraph{1.) When building the library I get an error message:}
\begin{itemize}
\item \textbf{unrecognized command line option "-std=c++11"}\\
  This means that your compiler is too old. You can check the 
  version of your compiler using \texttt{g++ -v}. If the version is lower than
  \texttt{4.8} you need to get a newer compiler version.
\end{itemize}

### 2018-08-06 Examples/description.tex
Docu modifications related to the new Example 8
First running version of the network code
Testing access to git
Some modifications in the documention: institute TW, more remarks about draps when installing dope, etc.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Thomas Wick\thanks{École Polytechnique, 
    {thomas.wick@polytechnique.edu}}, 
  Winnifried Wollner\thanks{Technische Universität Darmstadt, 
    {wollner@mathematik.tu-darmstadt.de}}
}

\date{\today
\vspace*{2cm}
\begin{figure}[h]
\centering
{\includegraphics[width=8cm]{Documentation/logo.png}}
\end{figure}
}

@@

@@

>>>>

\usepackage{wallpaper} % Hintergrundbild ueber ganze Titelseite
\usepackage{eso-pic,transparent}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Thomas Wick\thanks{Leibniz Universit\"at Hannover, 
    {thomas.wick@ifam.uni-hannover.de}}, 
  Winnifried Wollner\thanks{Technische Universität Darmstadt, 
    {wollner@mathematik.tu-darmstadt.de}}
}

\date{\today
\vspace*{8.1cm}
%\begin{figure}[h]
%\centering
%{\includegraphics[width=8cm]{Documentation/logo.png}}
%\end{figure}
}

\transparent{1.0}{\ThisCenterWallPaper{0.5}{Documentation/logo.png}}
%\ThisTileWallPaper

@@

\subsection{PDEs on Networks}
\label{PDE_network}
\input{PDE/StatPDE/Example14/content.tex}

@@

\subsection{Fully monolithic phase-field fracture propagation}
\label{PDE_phase_field_fracture}
\input{PDE/InstatPDE/Example8/content.tex}
